---
title: "Assignment3"
author: "ZIHAN TAN"
date: "8/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#library(caret)
library(Hmisc)
library(SASxport)
library(smbinning)
library(InformationValue)
library(pROC)
```
#read
```{r}
data(diabete_df)
lookup.xport("DIQ_I.XPT")
diabete_df <- read.xport("DIQ_I.XPT")
diabete_df$DIQ010[diabete_df$DIQ010!=1]<-0

```
#use demographic and diatiery information to predict diabettes using logistic regression model
#combine three df
```{r}
data(demo_df)
lookup.xport("DEMO_I.XPT")
demo_df <- read.xport("DEMO_I.XPT")
data(diet_df)
lookup.xport("DR1TOT_I.XPT")
diet_df <- read.xport("DR1TOT_I.XPT")
information <- merge(demo_df, diet_df, by.x = "SEQN", by.y= "SEQN")
newdiabete <- diabete_df[0:2]
df <- merge(information,newdiabete, by.x = "SEQN", by.y = "SEQN")
df$RIAGENDR <- factor(df$RIAGENDR)
df$RIDRETH1 <- factor(df$RIDRETH1)
df$DMDEDUC2[is.na(df$DMDEDUC2)]<-0
df$DMDEDUC2 <- factor(df$DMDEDUC2)
df$DR1TRET[is.na(df$DR1TRET)]<-0
df$DR1TVARA[is.na(df$DR1TVARA)]<-0
df$DR1TACAR[is.na(df$DR1TACAR)]<-0
df$DR1TLYCO[is.na(df$DR1TLYCO)]<-0
df$DR1TVB1[is.na(df$DR1TVB1)]<-0
df$DR1TNIAC[is.na(df$DR1TNIAC)]<-0

TotalDataFrame <- df[,c("DIQ010","RIAGENDR","RIDAGEYR","RIDRETH1","DMDEDUC2","DMDHHSIZ","DR1TRET","DR1TVARA","DR1TACAR","DR1TLYCO","DR1TVB1","DR1TNIAC")]

```
#randomly split data into training(70%) and testing set (30%)
```{r}
dt <- sort(sample(nrow(TotalDataFrame),nrow(TotalDataFrame)*.7))
train<- TotalDataFrame[dt,]
test<-TotalDataFrame[-dt,]
```
#use demographic and diatiery information to predict diabettes using LR model
# I used the following dependent variables: race, gender, age in years at screening, education level, household number, retinol, Vitamin A RAE, Alpha-carotene, Lycopene, Thiamin, Niacin.
```{r}
logitMod <- glm(DIQ010 ~ RIDAGEYR + DMDHHSIZ + DR1TRET + DR1TVARA + DR1TACAR + DR1TLYCO + DR1TVB1 + DR1TNIAC + RIAGENDR + RIDRETH1 + DMDEDUC2, data=train,family = 'binomial')
#summary(logitMod)
predicted <- plogis(predict(logitMod, test))  # predicted scores
```
# The following variables: DMDHHSIZ, DR1TRET, DR1TVARA, DR1TACAR, DR1TLYCO, DR1TVB1, DR1TNIAC did not obtain significant p-values which means that our logisitic model could be improved by deleting these variables.

# Measure performance of the LR model using accuracy  ( use 0.5 as threshold), show values
```{r}
error <- misClassError(test$DIQ010, predicted, threshold = 0.5)
accuracy <- 1-error
print(accuracy)
```
#measure performance of the LR model using AUCROC( use library), plot the ROC curve
```{r}
library(AUC)
plotROC(test$DIQ010,predicted)
```
#measure performance of the LR model using confusion matrix, print the matrix
```{r}
matrix <- confusionMatrix(test$DIQ010, predicted, threshold = 0.5)
matrix
```

